Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-15 paper.tex
More content

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
Implementing a Revolutionary Novel Desktop-as-a-Service}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun\orcidID{0000-1111-2222-3333} \and
Johannes Bouché\orcidID{1111-2222-3333-4444}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering, Frankfurt University of Applied Sciences,\\
Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper will cover very novel and non-published knowledge we gained
from developing and implementing a DaaS that is funded by the German
Federal Ministry for Economic Affairs and Climate Action. The topic
fits very well into the topics of the conference.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.
% 
% Subsequent paragraphs, however, are indented.

\subsection{Motivation}

@@

@@

TODO: Christian

@@

@@

TODO Christian: Latenz bei Cloud-Gaming Erfahrungen

@@

@@

@@

@@

\newpage

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.

\begin{credits}
\subsubsection{\ackname} A bold run-in heading in small font size at the end of the paper is
used for general acknowledgments, for example: This study was funded
by X (grant number Y).

\subsubsection{\discintname}
It is now necessary to declare any competing interests or to specifically
state that the authors have no competing interests. Please place the
statement with a bold run-in heading in small font size beneath the
(optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
system, is used, then the disclaimer can be provided directly in the system.},
for example: The authors have no competing interests to declare that are
relevant to the content of this article. Or: Author A has received research
grants from Company W. Author B has received a speaker honorarium from
Company X and owns stock in Company Y. Author C is a member of committee Z.
\end{credits}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}, last accessed 2023/10/25
\end{thebibliography}
\end{document}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
Implementing a Revolutionary Novel Desktop-as-a-Service}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun\orcidID{0009-0004-9955-3752} \and
Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering, Frankfurt University of Applied Sciences,\\
Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper will cover very novel and non-published knowledge we gained
from developing and implementing a DaaS that is funded by the German
Federal Ministry for Economic Affairs and Climate Action. The topic
fits very well into the topics of the conference. TODO: Christian

\keywords{DaaS \and Compatibility \and Performance \and Stability \and Usability}
\end{abstract}
%
%
%
\section{Introduction}

Inkl. Motivation

TODO: Christian (1)
TODO: Johannes (2)

@@

TODO: Christian (1)
TODO: Johannes (2)

@@

TODO: Christian (1)
TODO: Johannes (2)

@@

TODO: Johannes (1)
TODO: Christian (2)
TODO Christian: Latenz bei Cloud-Gaming Erfahrungen

@@

Ceph-Dateisystem

Datenbank SQlite aktuell. Perspektivisch MariaDB

Guacamole läuft 1x direkt auf dem Host aktuell. Läuft theoretisch auf jedem Host.

@@

TODO: Johannes (1)
TODO: Christian (2)

@@

Ceph-Dateisystem

Datenbank SQlite aktuell. Perspektivisch MariaDB

Guacamole läuft 1x direkt auf dem Host aktuell. Läuft theoretisch auf jedem Host. Proxmox kann sich darum kümmern?!

@@

TODO Johannes: Beschreibung zur Position der Komponenten, Möglichkeiten der Parallelisierung und Einschränkungen

@@

TODO: Christian (1)
TODO: Johannes (2)

Ideen und Konzepte zur Trennung von User und Admin-Ansicht

Reduktion der Komplexität der Bedienung durch Fokus auf notwendigste Interaktionsschritte

Desktop vs. einzelne Anwendung im Browser-Tab

Anpassung des Browser-Inhalts auf die Größe der Anwendung

Herausforderungen, Entwicklung, Implementierung, Lessons-learned

TODO Johannes: Erlebnisse der letzten 3-4 Wochen aufschreiben

\section{Conclusion}

TODO: Zusammen am Schluss

\section{Outlook}

TODO: Zusammen am Schluss

\section*{Acknowledgements}

This work was funded by the Federal Ministry for Economic Affairs and Climate Action
('\textsl{Bundesministerium f\"ur Wirtschaft und Klimaschutz}')
in the framework of the central innovation programme
for small and medium-sized enterprises
('\textsl{Zentrales Innovationsprogramm Mittelstand}').

We thank our project partners from Nuromedia GmbH for their support.
We especially thank Björn Goetschke, Mike Ludemann, Dario Savella, Holger Sprengel, and Rahul Tomar.

\section*{References}

% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%

% \bibliography{\jobname_no_dashes_at_repeated_names,references}{}

\end{document}
